Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-04-24 extended_catalog/paper/extended_search.tex
updated text

% New text is included inside of the \newtext command
% and is bold and red
\newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
% To unformat the new text, comment out the above line
% and include hte line below
% \newcommand{\newtext}[1]{#1}

@@

 For these reasons, in Section~\ref{analysis_methods_section}
we present a new systematic method for analyzing spatially extended
LAT sources.  
\newtext{
In Section~\ref{monte_carlo_validation}, we demonstrate
that this method can be used to test the statistical significance of the
extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
we asses the bias that is is introduced by using an incorrect spatial model.
In Section~\ref{extension_sensitivity}
we calculate the LAT detection threshold to resolve the extension
of a source.}
In Section~\ref{dual_localization_method}, we
study the ability of the LAT to 
distinguish between a single extended source and unresolved closely-spaced point-like sources
In Section~\ref{test_2lac_sources}, we further demonstrate that our
detection method does not misidentify point-like sources as being
extended by testing the extension of active Galactic nuclei (AGN)
believed to be unresolvable.  In Section~\ref{validate_known},
we systematically reanalyze the twelve extended sources included
in the 2FGL catalog and in Section~\ref{systematic_errors_on_extension}
we describe a way to estimate systematic errors on the measured extension of a source.
In Section~\ref{extended_source_search_method}, we
describe a search for new spatially extended LAT sources. Finally,
in Section~\ref{new_ext_srcs_section} we present the detection of the
extension of nine spatially extended sources that were reported in the 2FGL catalog
but treated as point-like in the analysis.  Two of these sources have been previously analyzed in
dedicated publications.

@@

For sources that are comparable in size to the PSF,
the differences in the PDF for
different spatial models are lost in the noise and the LAT is not sensitive
to the detailed spatial structure of these sources.  
\newtext{In section \ref{bias_wrong_spatial_model}, we perform a dedicated Monte Carlo simulation
to asses possible bias due to incorrectly modeling the spatial structure
of an extended source.}
Therefore, in our
search for extended sources we use only a radially-symmetric uniform
disk spatial model. Unless otherwise noted,
we quote the radius to the edge ($\sigma$) as the size of the source.

@@

\newtext{
These previous simulations spaned the range of detectable fluxes 
over two different energy ranges, but only assuming an isotropic backgorund.
We performed a second simulation to assess any effects that could
be introduces by performing this test in the presence of a highly
structured background.
Our simulation setup was the same as above except that the sources
were simulated on top of and analytized assuming the presence of
the standard Galactic and isotropic diffuse background model used
in 2FGL.

@@

To limit the number of tests, we selected only one flux
level for each of the four spectral indices and we perform
this test only in the 1 \gev to 100 \gev energy range. 
The source flux was selected so that $\ts\sim50$. This is around 
the significane level for which on might
exepcted to be able to spatially resolve the source. 
We do not test brigher sources since the structured background
should produce the most significant effect for very bright sources.

Because the Galactic diffuse emission is highly structure, the point-source
sensitivity can vary signficantly across the galactic plane.
To account for this, we scaled the flux (for a given spectral index)
by the overal background level according to this formula:
\begin{equation}
  \label{scale_flux_by_background}
  F(\vec{x}) = F(\text{GC}) \times \left(
  \frac{B(\text{GC})}{B(\vec{x})}\right)^{1/2}.
\end{equation}
Here, $\vec{x}$ is the position of the source, $F$ is the integral
flux of the simulated source from 100 \mev to 100 \gev, $F(\text{GC})$
is the same quantity if the source were at the galactic center, $B$
is the integral of the Galactic diffuse and isotropic diffuse emission
model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quanitty
if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
tabulates $F(\text{GC})$ and the average \ts for the four spectral models.
For each spectral index, we performed $\sim90,000$ simulations.

@@

\newtext{
We performed a Monte Carlo study to asses the biases introudced by incorreclty
modeling the spatial structure of an extended source. This is important because any assumed spatial
model is just an approximation to the true photon distribution of the source.

To assess this systematic, we simulated the spatially extended ring-type SNR W44.
W44 was slelected because it is the most signfiicant extended source detected by the LAT 
that has been reported as having a non-radially symmetric photon-distribution \cite{w44}.

W44 was simulated with a power-law spectral model. The flux and spectral index of this source
were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
and summarized in Table~\ref{known_extended_sources}. In particualr W44 was simulated
with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
index of 2.66.

@@

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but the souce was simulated on
top of and analyzed assuming the presence of the standard galactic and
isotropic diffuse background model used in 2FGL.  This simulation was
in the 1 \gev to 100 \gev energy range and
the sources were simulated over the two-year time range included in the
2FGL catalog. We performed 985 identical simulations with different seeds to
see the statistical spread in the fit values.

After simulating the ring-like source, we fit the spectral and spatial parametesr of 
the ring-like extended source with successivly more complicated spatial models.
We obtained the best fit spatial parameters using \pointlike and, using 
these best fit spatial paramters, obtained the best fit spectral paramters 
using \gtlike. In total, we performed the fit using a point-like spatial model,
using a radially-symmetric uniform Gaussian and disk spatial model, 
an Elliptical disk spatial model, and finally the Monte Carlo true Elliptical
ring spatial model.

Figure~\ref{ts_comparison_w44sim} shows the the distribution of TS values for 
each of the simluations when fitting the simulated sources 
with the different spatial models. 
Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
fitting the simulated Elliptical ring extended source as as a point-like source.
the source is very significant as a point source ($\ts\sim3500$).
Figure~\ref{ts_comparison_w44sim}b shows the distirbution of \tsext values
when fitting the source as a radially-symmetric uniform disk or Gaussian source.
The source is very significiantly extended ($\tsext\sim250$). 
On average \tsext is slightly larger when
fitting the source with the Disk spatial model compared to the Gaussian spatial model.
Considering that the simulated source's true spatial model has a sharp edge, it
makes sense that the Disk would provide a better fit.

@@

Figure~\ref{bias_w44sim} shows the distirbution of best fit parameters
for these simulations. Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
show the distribututions of best fit flux and spectral indices.
They show that when fitting this simulated extended source with a point-like
spatial model, there is a $\sim$10\% bias in the fit flux and
$\sim5\%$ bias in the fit index. But when fitting the sources with any of
the extended spatial models, there is no bias in the best fit spectral parameters
(within the precision of this Monte Carlo study. The reason for this is
because within the finite angular precision and limited statsitics of the LAT, 
all of the extended spatial models can be ajusted to look almost the same.
For brighter or larger sources, this could potentially be a larger effect.

Figure~\ref{bias_w44sim}c plots the best fit 68\% contaiment radius
(\rsixeight).  For the elliptical ring spatial model, as expected
there is no significant bias in the best fit size. What is surprising
is that for none of the tested spatial models was the bias greater
than $\sim10\%$. This shows that for whatever spatial model is used,
the best fit \rsixeight is a reasonable measure of the true 68\%
containment radius.

@@

2FGL\,J0851.7$-$4635 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Vela Jr. This source was recently studied by the LAT
Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
contours of Vela Jr. \citep{vela_jr_hess}.
There are three
point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
and 2FGL\,J0855.4$-$4625 which correlate with the 
multiwavelength
emission of
this SNR but do not appear to be physically distinct sources.
They were most likely included in the 2FGL catalog to compensate for residuals
induced by not modeling the extension of Vela Jr. and were removed
from our model of the sky.

@@

\startdata
\multicolumn{6}{c}{Isotropic Background} \\
\hline
      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
      \hline
        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
      \hline
      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
      \hline                                                
        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
\cutinhead{Galactic and Isotropic Diffuse Background\tablenotemark{(b)}}
      1.5 &  $3\times 10^{-7}$ &           90741 &     63    &   \nodata   & \nodata     \\
        2 &          $10^{-6}$ &           92161 &     60    &   \nodata   & \nodata     \\
      2.5 &  $3\times 10^{-6}$ &           86226 &     47    &   \nodata   & \nodata    \\
        3 &          $10^{-5}$ &           94412 &     61    &   \nodata   & \nodata    \\
\enddata

@@

\clearpage
\begin{deluxetable}{lr}
\tablecolumns{2}
\tablewidth{0pt}
\tablecaption{Nearby Residual Sources
\label{fake_2fgl_sources}
}
\tablehead{
\colhead{Extended Source}&
\colhead{Nearby Residual Sources}
}
\startdata
\hline
2FGL\,J0823.0$-$4246    & 2FGL\,J0823.4$-$4305, 2FGL\,J0821.0$-$4254 \\
2FGL\,J1627.0$-$2425c   & \nodata \\
2FGL\,J0851.7$-$4635    & 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, 2FGL\,J0855.4$-$4625 \\
2FGL\,J1615.0$-$5051    & \nodata \\
2FGL\,J1615.2$-$5138    & 2FGL\,J1614.9$-$5212  \\
2FGL\,J1632.4$-$4753c   & 2FGL\,J1634.4$-$4743c \\
2FGL\,J1712.4$-$3941    & \nodata \\
2FGL\,J1837.3$-$0700c   & 2FGL\,J1835.5$-$0649 \\
2FGL\,J2021.5+4026      & 2FGL\,J2019.1+4040 \\
\enddata

@@

\begin{figure}
    \ifcolorfigure
      \plotone{source_plots/source_Puppis_A_color.eps}
    \else
      \plotone{source_plots/source_Puppis_A_bw.eps}
    \fi
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v8/run.py
  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
  of 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
  Gaussian kernel.  The triangular marker 
  (colored red in the online version)
  represents the 2FGL position of this source.  The plus-shaped
  marker and the circle (colored
  red) represent 
  the best fit position and extension of this source assuming a
  radially-symmetric uniform disk model.  The two 
  star-shaped markers (colored
  green) represent 2FGL sources that were
  removed from the background model.
  \newtext{From left to right, these sources are, from left to right,
  2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.}
  The lower right inset is the model predicted emission from a point-like
  source with the same spectrum as 2FGL\,J0823.4$-$4305 smoothed by the
  same kernel.  This source is spatially coincident with the Puppis A
  SNR. The light blue contours correspond to the X-ray image of Puppis
  A observed by \rosat \citep{rosat_puppis_a}.
  }\label{1FGL_J0823.3-4248}
\end{figure}

@@

\begin{figure}
    \ifcolorfigure
      \plotone{source_plots/source_HESS_J1837-069_color.eps}
    \else
      \plotone{source_plots/source_HESS_J1837-069_bw.eps}
    \fi
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v8/run.py
  \caption{
  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg15 2D Gaussian
  kernel and (b) with the emission from the background sources subtracted.
  The triangular marker (colored red in the online version) represents
  the 2FGL
  position of this source. 
  The plus-shaped marker and 
  the circle (colored red) represent the best fit position and extension
  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform disk model. 
  The circular and square-shaped markers (colored
  blue) represent the 2FGL and the relocalized positions respectively of
  two background 2FGL sources subtracted in (b).  The star-shaped marker
  (colored green) represents 2FGL\,J1835.5$-$0649, another 2FGL source that was removed from the
  background model.  The contours (colored light blue) correspond to
  the \tev image of HESS\,J1837$-$069
  \citep{hess_plane_survey}.
  The diamond-shaped marker (colored orange) represents the position of PSR\,J1838$-$0655
  and the hexagonal-shaped marker (colored purple) represents the position AX\,J1837.3$-$0652
  \citep{pulsations_HESS_J1837-069}.
  }\label{1FGL_J1837.5-0659c}
\end{figure}

>>>>

% New text is included inside of the \newtext command
% and is bold and red
\newcommand{\newtext}[1]{{\bfseries \color{red}#1}}
% To unformat the new text, comment out the above line
% and include the line below
% \newcommand{\newtext}[1]{#1}

@@

 For these reasons, in Section~\ref{analysis_methods_section}
we present a new systematic method for analyzing spatially extended
LAT sources.  
\newtext{
In Section~\ref{monte_carlo_validation}, we demonstrate
that this method can be used to test the statistical significance of the
extension of a LAT source and in Section~\ref{bias_wrong_spatial_model}
we asses the bias that is introduced by using an incorrect spatial model.
In Section~\ref{extension_sensitivity}
we calculate the LAT detection threshold to resolve the extension
of a source.}
In Section~\ref{dual_localization_method}, we
study the ability of the LAT to 
distinguish between a single extended source and unresolved closely-spaced point-like sources
In Section~\ref{test_2lac_sources}, we further demonstrate that our
detection method does not misidentify point-like sources as being
extended by testing the extension of active Galactic nuclei (AGN)
believed to be unresolvable.  In Section~\ref{validate_known},
we systematically reanalyze the twelve extended sources included
in the 2FGL catalog and in Section~\ref{systematic_errors_on_extension}
we describe a way to estimate systematic errors on the measured extension of a source.
In Section~\ref{extended_source_search_method}, we
describe a search for new spatially extended LAT sources. Finally,
in Section~\ref{new_ext_srcs_section} we present the detection of the
extension of nine spatially extended sources that were reported in the 2FGL catalog
but treated as point-like in the analysis.  Two of these sources have been previously analyzed in
dedicated publications.

@@

For sources that are comparable in size to the PSF,
the differences in the PDF for
different spatial models are lost in the noise and the LAT is not sensitive
to the detailed spatial structure of these sources.  
\newtext{In section \ref{bias_wrong_spatial_model}, we perform a dedicated Monte Carlo simulation
to asses possible bias due to incorrectly modeling the spatial structure
of an extended source.
In our search for extended sources we use only a radially-symmetric uniform
disk spatial model. Unless otherwise noted,
we quote the radius to the edge ($\sigma$) as the size of the source.}

@@

\newtext{
These simulations spanned the range of detectable fluxes 
over two different energy ranges, but only assuming an isotropic background.
We performed a second simulation to assess any effects that could
be introduces by performing this test in the presence of a highly
structured background.
Our simulation setup was the same as above except that the sources
were simulated on top of and analyzed assuming the presence of
the standard Galactic and isotropic diffuse background model used
in 2FGL.

@@

To limit the number of tests, we selected only one flux
level for each of the four spectral indices and we perform
this test only in the 1 \gev to 100 \gev energy range. 
The source flux was selected so that $\ts\sim50$. This is around 
the significance level for which on might
expect to be able to spatially resolve the source. 
We do not test brighter sources since the structured background
should produce the most significant effect for very bright sources.

Because the Galactic diffuse emission is highly structure, the point-source
sensitivity can vary significantly across the galactic plane.
To account for this, we scaled the flux (for a given spectral index)
so that the source always has approximatly the same signal-to-noise ratio:
\begin{equation}
  \label{scale_flux_by_background}
  F(\vec{x}) = F(\text{GC}) \times \left(
  \frac{B(\vec{x})}{B(\text{GC})}\right)^{1/2}.
\end{equation}
Here, $\vec{x}$ is the position of the source, $F$ is the integral
flux of the simulated source from 100 \mev to 100 \gev, $F(\text{GC})$
is the same quantity if the source were at the galactic center, $B$
is the integral of the Galactic diffuse and isotropic diffuse emission
model from 1 \gev to 100 \gev and $B(\text{GC})$ is the same quantity
if the source were at the galactic center.  Table~\ref{ts_ext_num_sims}
tabulates $F(\text{GC})$ and the average \ts for the four spectral models.
For each spectral index, we performed $\sim90,000$ simulations.

@@

\newtext{
We performed a Monte Carlo study to asses the biases introduced by incorrectly
modeling the spatial structure of an extended source. This is important because any assumed spatial
model is just an approximation to the true photon distribution of the source.

To assess this systematic, we simulated the spatially extended ring-type SNR W44.
W44 was selected because it is the most significant extended source detected by the LAT 
that has been reported as having a non-radially symmetric photon-distribution \cite{w44}.

W44 was simulated with a power-law spectral model. The flux and spectral index of this source
were taken from our re-analysis in this paper which is described in Section~\ref{validate_known}
and summarized in Table~\ref{known_extended_sources}. In particular W44 was simulated
with a flux of $7.12\times10^{-8}$ \phflux in the energy range from 1 \gev to 100 \gev with a spectral
index of 2.66.

@@

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but the source was simulated on
top of and analyzed assuming the presence of the standard galactic and
isotropic diffuse background model used in 2FGL.  This simulation was
in the 1 \gev to 100 \gev energy range and
the sources were simulated over the two-year time range included in the
2FGL catalog. We performed 985 identical simulations with different seeds to
see the statistical spread in the fit values.
In the simulations of W44, we disabled the inherent energy dispersion of photons
by the LAT. The bias caused by ignoring energy dispersion 
will be discussed in an upcoming paper by the LAT collaboration \citep{lat_on_orbit_psf}.

After simulating the ring-like source, we fit the spectral and spatial parameters of 
the ring-like extended source with successively more complicated spatial models.
We obtained the best fit spatial parameters using \pointlike and, using 
these best fit spatial parameters, obtained the best fit spectral parameters 
using \gtlike. In total, we performed the fit using a point-like spatial model,
using a radially-symmetric uniform Gaussian and disk spatial model, 
an Elliptical disk spatial model, and finally the Monte Carlo true Elliptical
ring spatial model.

Figure~\ref{ts_comparison_w44sim} shows the distribution of TS values for 
each of the simulations when fitting the simulated sources 
with the different spatial models. 
Figure~\ref{ts_comparison_w44sim}a shows the distribution of \ts values when 
fitting the simulated Elliptical ring extended source as as a point-like source.
the source is very significant as a point source ($\ts\sim3500$).
Figure~\ref{ts_comparison_w44sim}b shows the distirbution of \tsext values
when fitting the source as a radially-symmetric uniform disk or Gaussian source.
The source is very significiantly extended ($\tsext\sim250$). 
On average \tsext is slightly larger when
fitting the source with the Disk spatial model compared to the Gaussian spatial model.
Considering that the simulated source's true spatial model has a sharp edge, it
makes sense that the Disk would provide a better fit.

@@

Figure~\ref{bias_w44sim} shows the distirbution of best fit parameters
for these simulations. Figure~\ref{bias_w44sim}a and Figure~\ref{bias_w44sim}b
show the distribututions of best fit flux and spectral indices.
They show that when fitting this simulated extended source with a point-like
spatial model, there is a $\sim$10\% bias in the fit flux and
$\sim5\%$ bias in the fit index. But when fitting the sources with any of
the extended spatial models, there is no bias in the best fit spectral parameters
(within the precision of this Monte Carlo study. The reason for this is
because within the finite angular precision and limited statistics of the LAT, 
all of the extended spatial models can be adjusted to look almost the same.
For brighter or larger sources, this could potentially be a larger effect.

Figure~\ref{bias_w44sim}c plots the best fit 68\% containment radius
(\rsixeight).  For the elliptical ring spatial model, as expected
there is no significant bias in the best fit size. What is surprising
is that for none of the tested spatial models was the bias greater
than $\sim10\%$. This shows that for whatever spatial model is used,
the best fit \rsixeight is a reasonable measure of the true 68\%
containment radius.

@@

2FGL\,J0851.7$-$4635 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Vela Jr. This source was recently studied by the LAT
Collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
contours of Vela Jr. \citep{vela_jr_hess}.
There are three
point-like catalog sources 2FGL\,J0848.5$-$4535,
2FGL\,J0853.5$-$4711, and
2FGL\,J0855.4$-$4625
which correlate with the 
multiwavelength
emission of
this SNR but do not appear to be physically distinct sources.
They were most likely included in the 2FGL catalog to compensate for residuals
induced by not modeling the extension of Vela Jr. and were removed
from our model of the sky.

@@

\startdata
\multicolumn{6}{c}{Isotropic Background} \\
\hline
      1.5 &  $3\times 10^{-7}$ &           18938 &  22233    &     18938   &    8084     \\
          &          $10^{-7}$ &           19079 &   5827    &     19079   &    2258     \\
          &  $3\times 10^{-8}$ &           19303 &   1276    &     19303   &     541     \\
          &          $10^{-8}$ &           19385 &    303    &     19381   &     142     \\
          &  $3\times 10^{-9}$ &           18694 &     62    &     12442   &      43     \\
      \hline
        2 &          $10^{-6}$ &           18760 &  22101    &     18760   &    3033     \\
          &  $3\times 10^{-7}$ &           18775 &   4913    &     18775   &     730     \\
          &          $10^{-7}$ &           18804 &   1170    &     18803   &     192     \\
          &  $3\times 10^{-8}$ &           18836 &    224    &     15256   &      50     \\
          &          $10^{-8}$ &           17060 &     50    &   \nodata   & \nodata     \\
      \hline
      2.5 &  $3\times 10^{-6}$ &           18597 &  19036    &     18597   &     786    \\
          &          $10^{-6}$ &           18609 &   4738    &     18608   &     208    \\
          &  $3\times 10^{-7}$ &           18613 &    954    &     15958   &      53    \\
          &          $10^{-7}$ &           18658 &    203    &   \nodata   & \nodata    \\
          &  $3\times 10^{-8}$ &           14072 &     41    &   \nodata   & \nodata    \\
      \hline                                                
        3 &          $10^{-5}$ &           18354 &  19466    &     18354   &     215    \\
          &  $3\times 10^{-6}$ &           18381 &   4205    &     15973   &      54    \\
          &          $10^{-6}$ &           18449 &    966    &   \nodata   & \nodata    \\
          &  $3\times 10^{-7}$ &           18517 &    174    &   \nodata   & \nodata    \\
          &          $10^{-7}$ &           13714 &     41    &   \nodata   & \nodata    \\
\cutinhead{Galactic and Isotropic Diffuse Background\tablenotemark{(b)}}
      1.5 &  $2.3\times 10^{-8}$ &           90741 &     63    &   \nodata   & \nodata     \\
        2 &  $1.2\times 10^{-7}$ &           92161 &     60    &   \nodata   & \nodata     \\
      2.5 &  $4.5\times 10^{-7}$ &           86226 &     47    &   \nodata   & \nodata    \\
        3 &  $2.0\times 10^{-6}$ &           94412 &     61    &   \nodata   & \nodata    \\
\enddata

@@

\clearpage
\begin{deluxetable}{lr}
\tablecolumns{2}
\tablewidth{0pt}
\tablecaption{Nearby Residual Sources
\label{fake_2fgl_sources}
}
\tablehead{
\colhead{Extended Source}&
\colhead{Nearby Residual Sources}
}
\startdata
\hline
2FGL\,J0823.0$-$4246    & 2FGL\,J0821.0$-$4254, 2FGL\,J0823.4$-$4305 \\
2FGL\,J1627.0$-$2425c   & \nodata \\
2FGL\,J0851.7$-$4635    & 2FGL\,J0848.5$-$4535, 2FGL\,J0853.5$-$4711, 2FGL\,J0855.4$-$4625 \\
2FGL\,J1615.0$-$5051    & \nodata \\
2FGL\,J1615.2$-$5138    & 2FGL\,J1614.9$-$5212  \\
2FGL\,J1632.4$-$4753c   & 2FGL\,J1634.4$-$4743c \\
2FGL\,J1712.4$-$3941    & \nodata \\
2FGL\,J1837.3$-$0700c   & 2FGL\,J1835.5$-$0649 \\
2FGL\,J2021.5+4026      & 2FGL\,J2019.1+4040 \\
\enddata

@@

\begin{figure}
    \ifcolorfigure
      \plotone{source_plots/source_Puppis_A_color.eps}
    \else
      \plotone{source_plots/source_Puppis_A_bw.eps}
    \fi
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v8/run.py
  \caption{A diffuse-emission-subtracted 1 \gev to 100 \gev counts map
  of 2FGL\,J0823.0$-$4246 smoothed by a 0\fdg1 2D
  Gaussian kernel.  The triangular marker 
  (colored red in the online version)
  represents the 2FGL position of this source.  The plus-shaped
  marker and the circle (colored
  red) represent 
  the best fit position and extension of this source assuming a
  radially-symmetric uniform disk model.  The two 
  star-shaped markers (colored
  green) represent 2FGL sources that were
  removed from the background model.
  \newtext{From left to right, these sources are 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254.}
  The lower right inset is the model predicted emission from a point-like
  source with the same spectrum as 2FGL\,J0823.4$-$4305 smoothed by the
  same kernel.  This source is spatially coincident with the Puppis A
  SNR. The light blue contours correspond to the X-ray image of Puppis
  A observed by \rosat \citep{rosat_puppis_a}.
  }\label{1FGL_J0823.3-4248}
\end{figure}

@@

\begin{figure}
    \ifcolorfigure
      \plotone{source_plots/source_HESS_J1837-069_color.eps}
    \else
      \plotone{source_plots/source_HESS_J1837-069_bw.eps}
    \fi
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v8/run.py
  \caption{
  A diffuse-emission-subtracted 10 \gev to 100 \gev counts map of the
  region around 2FGL\,J1837.3$-$0700c (a) smoothed by a 0\fdg15 2D Gaussian
  kernel and (b) with the emission from the background sources subtracted.
  The triangular marker (colored red in the online version) represents
  the 2FGL
  position of this source. 
  The plus-shaped marker and 
  the circle (colored red) represent the best fit position and extension
  of 2FGL\,J1837.3$-$0700c assuming a radially-symmetric uniform disk model. 
  The circular and square-shaped markers (colored
  blue) represent the 2FGL and the relocalized positions respectively of
  two background 2FGL sources subtracted in (b).  \newtext{The star-shaped marker
  (colored green) represents 2FGL\,J1835.5$-$0649, another 2FGL source that was removed from the
  background model.}  The contours (colored light blue) correspond to
  the \tev image of HESS\,J1837$-$069
  \citep{hess_plane_survey}.
  The diamond-shaped marker (colored orange) represents the position of PSR\,J1838$-$0655
  and the hexagonal-shaped marker (colored purple) represents the position AX\,J1837.3$-$0652
  \citep{pulsations_HESS_J1837-069}.
  }\label{1FGL_J1837.5-0659c}
\end{figure}
